---
title: "Capstone Explore"
author: "Michael Pearson"
date: "7/28/2017"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(R.utils)
library(tm)
library(SnowballC)     
library(MASS)
eng_news <- read_file("/Users/mutecypher/Documents/Documents - Michael’s iMac/Coursera/Capstone Project/files/en_US/en_US.news.txt")
nchar(eng_news)
eng_blogs <- read_file("/Users/mutecypher/Documents/Documents - Michael’s iMac/Coursera/Capstone Project/files/en_US/en_US.blogs.txt")
nchar(eng_blogs)
eng_twitter <- read_file("/Users/mutecypher/Documents/Documents - Michael’s iMac/Coursera/Capstone Project/files/en_US/en_US.twitter.txt")
nchar(eng_twitter)
blog_us <- file("/Users/mutecypher/Documents/Documents - Michael’s iMac/Coursera/Capstone Project/files/en_US/en_US.blogs.txt")
tweet_us <- file("/Users/mutecypher/Documents/Documents - Michael’s iMac/Coursera/Capstone Project/files/en_US/en_US.twitter.txt")
news_us <- file("/Users/mutecypher/Documents/Documents - Michael’s iMac/Coursera/Capstone Project/files/en_US/en_US.news.txt")
newslines <- countLines("/Users/mutecypher/Documents/Documents - Michael’s iMac/Coursera/Capstone Project/files/en_US/en_US.news.txt")
bloglines <- countLines("/Users/mutecypher/Documents/Documents - Michael’s iMac/Coursera/Capstone Project/files/en_US/en_US.blogs.txt")
tweetlines <- countLines("/Users/mutecypher/Documents/Documents - Michael’s iMac/Coursera/Capstone Project/files/en_US/en_US.twitter.txt")
blog25 <- readLines(blog_us, 25)
tweet25 <- readLines(tweet_us, 25)
news25 <- readLines(news_us, 25)
close(news_us)
close(blog_us)
close(tweet_us)
```

## R Markdown

Beginning of text processing
```{r count chars}
newzchar <- nchar(news25)
sumnew <- sum(newzchar)
tweetchar <- nchar(tweet25)
sumtweet <- sum(tweetchar)
blogchar <- nchar(blog25)
sumblog <- sum(blogchar)
```

## Counting characters

There are `r sumnew` characters in the first 25 lines of news.

There are `r sumtweet` characters in the first 25 lines of blogs.

There are `r sumblog` characters in the first 25 lines of tweets.

### Counting lines

There are `r tweetlines` lines in en_US.twitter.txt.

There are `r bloglines` lines in en_US.blogs.txt


There are `r newslines` lines in en_US.news.txt.

```{r for quiz 1}
tweet_us <- file("/Users/mutecypher/Documents/Documents - Michael’s iMac/Coursera/Capstone Project/files/en_US/en_US.twitter.txt")
tweet_all <- readLines(tweet_us, n= tweetlines, warn = FALSE, encoding = "UTF=8", skipNul = TRUE)
close(tweet_us)
length(grep("A computer once beat me at chess, but it was no match for me at kickboxing", tweet_all))
length(grep("love", tweet_all))/length(grep("hate", tweet_all))
max(nchar(tweet_all[1:tweetlines]))
news_us <- file("/Users/mutecypher/Documents/Documents - Michael’s iMac/Coursera/Capstone Project/files/en_US/en_US.news.txt")
news_all <- readLines(news_us, n = newslines, warn = FALSE, encoding = "UTF=8", skipNul = TRUE)
close(news_us)
max(nchar(news_all[1:newslines]))
blog_us <- file("/Users/mutecypher/Documents/Documents - Michael’s iMac/Coursera/Capstone Project/files/en_US/en_US.blogs.txt")
blog_all <- readLines(blog_us, n= bloglines, warn = FALSE, encoding = "UTF=8", skipNul = TRUE)
close(blog_us)
max(nchar(blog_all[1:bloglines]))
```
## new section - loading and other fun
```{r get it in}
bwlines <- countLines("/Users/mutecypher/Documents/Documents - Michael’s iMac/Coursera/Capstone Project/files/full-list-of-bad-words-banned-by-google-txt-file_2013_11_26_04_53_31_867.txt")
badwords <- readLines("/Users/mutecypher/Documents/Documents - Michael’s iMac/Coursera/Capstone Project/files/full-list-of-bad-words-banned-by-google-txt-file_2013_11_26_04_53_31_867.txt", n= bwlines, warn = FALSE, encoding = "latin1", skipNul = FALSE)
set.seed(1151960)
samp_per <- 0.1
sam_twit <- tweet_all[sample(1:length(tweet_all),samp_per*length(tweet_all))]
sam_news <- news_all[sample(1:length(news_all),samp_per*length(news_all))]
sam_blog <- blog_all[sample(1:length(blog_all),samp_per*length(blog_all))]
use_this <- c(sam_blog,sam_news, sam_twit)
sam_Corpus <- VCorpus(VectorSource(use_this))
docs <- tm_map(sam_Corpus, removePunctuation)
docs$word <- gsub("[^[:alpha:]]", "", docs$word) 
##for (j in seq(docs)) {
##    docs[[j]] <- gsub("/", " ", docs[[j]])
##    docs[[j]] <- gsub("@", " ", docs[[j]])
##    docs[[j]] <- gsub("\\|", " ", docs[[j]])
##    docs[[j]] <- gsub("\u2028", " ", docs[[j]])
##    docs[[j]] <- gsub("#", " ", docs[[j]])
##}
docs <- tm_map(docs, removeNumbers)
docs <- tm_map(docs, tolower)   
docs <- tm_map(docs, PlainTextDocument)
DocsCopy <- docs
docs <- tm_map(docs, removeWords, stopwords("english"))  
docs <- tm_map(docs, removeWords, badwords)
docs <- tm_map(docs, PlainTextDocument)
## Now let's make a version Potter's stemming algorithm
foodocs <- tm_map(docs, stemDocument)
foodocs <- tm_map(foodocs, PlainTextDocument)
## remove the whitespaces from both types
docs <- tm_map(docs, stripWhitespace)
foodocs <- tm_map(foodocs, stripWhitespace)
foodocs <- tm_map(foodocs, PlainTextDocument)
docs <- tm_map(docs, PlainTextDocument)
```

``` {r file fun}
if(!file.exists("/Users/mutecypher/Documents/Documents - Michael’s iMac/Coursera/Capstone Project/files/dtm_foodocs.csv")){
dtm_foodocs <- DocumentTermMatrix(foodocs)
sparse_foodocs <- removeSparseTerms(dtm_foodocs, 0.1)
write.csv(as.matrix(sparse_foodocs), file = "/Users/mutecypher/Documents/Documents - Michael’s iMac/Coursera/Capstone Project/files/dtm_foodocs.csv")
}
sparse_foodocs <- read.csv("/Users/mutecypher/Documents/Documents - Michael’s iMac/Coursera/Capstone Project/files/dtm_foodocs.csv")
if(!file.exists("/Users/mutecypher/Documents/Documents - Michael’s iMac/Coursera/Capstone Project/files/tdm_foodocs.csv")){
tdm_foodocs <- TermDocumentMatrix(foodocs)
tdm_sparse_foodocs <- removeSparseTerms(tdm_foodocs, 0.1)
write.csv(as.matrix(tdm_sparse_foodocs), file = "/Users/mutecypher/Documents/Documents - Michael’s iMac/Coursera/Capstone Project/files/tdm_foodocs.csv")
}
tdm_sparse_foodocs <- read.csv("/Users/mutecypher/Documents/Documents - Michael’s iMac/Coursera/Capstone Project/files/tdm_foodocs.csv")
```

